### 2025-09-25 paper/sec/evaluation.tex
Rehash Eval intro.

\subsection{Success Rate by Category}
To evaluate the system we used a sample of the \SciGen dataset~\citep{moosavi21}. We aggregated the generated
expression in three categories: aggregation, trends, quantitative (See
Table~\ref{tab:natural-language-forms}). \figref{success_rate_by_category} shows the results obtained in
generating expression by categories.

@@

@@

In this section, we report the experimental results.
Table \ref{tab:results_combined} summarizes the performance of \gptfour and the most recent OpenAI model, \gptfive, under two different settings: with target-value sharing enabled and without target-value sharing.
Overall, the system produced a valid Fluid expression in 74.9\% of the cases (S.D. 3\%).

>>>>

@@

To evaluate the system we used a sample of the \SciGen dataset~\citep{moosavi21}. We aggregated the generated
expression in the linguistic categories from Table~\ref{tab:natural-language-forms}.
\figref{success_rate_by_category} shows the results obtained in generating expression by categories.

@@

Table \ref{tab:results_combined} summarizes the performance of \gptfour and the most recent OpenAI model,
\gptfive, under two different settings: with target-value sharing enabled and without target-value sharing.
Overall, the system produced a valid Fluid expression in 74.9\% of the cases (S.D. 3\%).
